---
title: "R-Studio Tutorial"
author: "Student No: 52102609"
date: "02/12/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Comment: If I have time complete the following - design of document, colour, images.
***

## 1. Introduction

***

## 2. RMarkdown

***

## 3. Data Preparation

Before we can start to prepare data we need to complete the follow steps 3.1 - 3.3. 

### 3.1 Install the packages
First you want to install the packages you will need to work with the data. I have already installed the packages so for you, you would enter the following code.

* Start a new markdown file (2.2.1)  
* Start a new code chunk (2.2.3)

Then type in the following code.

**install.packages(tidyverse)**  
**install.packages(here)**

### 3.2 Read the packages into R

```{r 3.1 Read in the Packages, message=FALSE, warning=FALSE}
# These are the packages we will use to work with the data.
library(tidyverse)
library(here)
```




### 3.3 Read in the data sets

R-Software is case sensitive, so if you name an object with all lower case letters, R will only recognise the name in this form.

Explain objects and assignment operators

```{r 3.1 Read in the data sets, message=FALSE, warning=FALSE}
demographics<-read_csv(here("2021-12-02_PU5050_Assessment_Input/2021-12-02_PU5050_Demographics.csv"))
ImagingWaitTimes<-read_csv(here("2021-12-02_PU5050_Assessment_Input/2021-12-02_PU5050_ImagingWaitTimes.csv"))
```

### 3.4 Inspect the data

Now that we have the data loaded into R, using the object names demographics and ImagingWaitTimes, we can start to inspect the data. Let's look at demographics first..

```{r 3.4.1 Glimpse}
# We will use a function called glimpse to look at the variable names within the data set
glimpse(demographics)
```

We can see that the data has 4 columns: chi, dob, sex and city.
Explain double/character

Another function to look at the data 

```{r 3.4.2 Head}
head(demographics)
```
Again we can see there are 4 groups and the types of data.

Now that we have an understanding of the variable names and type of variables we need to look in more detail for missing values, NA, and any unusual data values. 

```{r}
demographics%>%
  summarise_all(~sum(is.na(.)))
```



***

## 4. Data Visualisation

***

## 5. Summary and Reflection

***
