---
title: "TutorialDesignPlan"
author: "Debbie Cannon"
date: "11/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Introduction  
(Scenario - **What is the average waiting time in days for CT scans for each Scottish city in October 2021?**)

Discuss the metadata and data dictionary

### Objectives
* What are the benefits of reproducibility in science? 
* Why use R?

## 2. R markdown
### Objectives
* What is R markdown and why is it useful for reproducible science? 
Explain the following: 
* file header means
* how to add text and code chunks
* basic formatting in the text chunks (headers and lists) 
* how to include inline code
* how to specify the output file type
* how to build the output

## 3. Data Preparation
### Objectives
* What is the importance of good metadata? 
* Why are fake datasets useful? 
* What is the benefit of tidy datasets? 


```{r}
# Read in the datasets, inspect them, and remove errors and missing values. Join the two datasets.
```

## 4. Data Visualisation
### Objectives
* what are the main parameters ggplot uses for making graphs?

```{r}
# With your research question in mind, create at least one plot with default aesthetics improve it

```

* Explain the decisions you make in the text

## 5. Summary and Reflection
### Objectives
* What has been your experience using R for reproducible data analysis? 
* Please reflect on any problems or issues you encountered, for example whilst creating and merging datasets, or using the R language.


