---
title: "TutorialDesignPlan"
author: "Debbie Cannon"
date: "11/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Introduction  
(Scenario - **What is the average waiting time in days for Computer Tomography scans, for each Scottish city, in October 2021?**)

Discuss the metadata (Read Only, All data from 2021) and data dictionary

### Objectives
* What are the benefits of reproducibility in science? 

* Why use R?

## 2. R markdown
### Objectives
* 2.1 What is R markdown and why is it useful for reproducible science? 
Explain the following:
* 2.2.1 start new markdown file
* 2.2.2 file header means
* 2.2.3.how to add text and code chunks
* Pipe operator
* basic formatting in the text chunks (headers and lists) 
* how to include inline code
* how to specify the output file type
* how to build the output

## 3. Data Preparation
### Objectives
* What is the importance of good metadata? 
* Why are fake datasets useful? 
* What is the benefit of tidy datasets? 


```{r}
# Read in the datasets, inspect them, and remove errors and missing values. Join the two datasets.
#Install.packages
#How to show what packages are available
#library()
#Rproject
#here()
#read
#WaitingTimes
#Demographics
#glimpse
#head
#types of objects
#Search for number of NA
#Long method - new variables one column at a time
#short method - na.omit()
#summary - find largest and smallest
#date change object
#search for biggest and smallest dates (if only dates had been given explain method)
#explain different types of join 
#select join for this task
```

## 4. Data Visualisation
### Objectives
* what are the main parameters ggplot uses for making graphs?

```{r}
# With your research question in mind, create at least one plot with default aesthetics improve it
#create a bar chart

```

* Explain the decisions you make in the text

## 5. Summary and Reflection
### Objectives
* What has been your experience using R for reproducible data analysis? 
  + GitHub
  + Reading lots of theory - really need practice
* Please reflect on any problems or issues you encountered, for example whilst creating and merging datasets, or using the R language.
  + Over thinking the basics
  + Not focusing on what I expect to happen
  + Not having a logical plan
  + Had to slow down
  + Couldn't visualise how everything connected ie branches
  + RNotebook


